Datasheet for 'Exploring the Determinants of Body Weight: A Bayesian Analysis of Anthropometric and Demographic Factors Among Female U.S. Army Personnel

### 2024-12-11 other/datasheet/datasheet.qmd
update paper, scripts, references
Specify Clarification on Dataset Usage

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to investigate the relationship between body weight and anthropometric and demographic predictors among female U.S. Army personnel. It addresses the gap in research on female military personnel, particularly concerning their health, operational readiness, and body composition.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was created by the Natick Soldier Research, Development, and Engineering Center (NSRDEC) under the U.S. Army.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The dataset was funded by the U.S. Department of Defense as part of its efforts to improve operational readiness and health monitoring among military personnel.
4. *Any other comments?*
    - This dataset is one of the most comprehensive anthropometric surveys conducted on military personnel, focusing specifically on female soldiers.

@@

	- The dataset contains 1,986 instances, each representing one soldier.

@@

	- The target variable is body weight (in pounds), which is used to analyze its relationship with the predictors.

@@

@@

	- The dataset underwent preprocessing to remove noise and redundancies, ensuring high data quality.

@@

	- The dataset is self-contained and does not rely on external resources.

@@

	- No confidential information is included in the dataset.

@@

@@

	- Data was collected between 2010 and 2012, aligning with the time when the measurements were taken.

@@

	- Ethical considerations were likely reviewed as part of the U.S. Army's internal processes for human data collection, though explicit documentation is not provided.

@@

	- Website.

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Cannot find any. 
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- Cannot find any. 
3. *What (other) tasks could the dataset be used for?*
	- The dataset could be used for health monitoring, ergonomic research, fitness program optimization, and studies on gender-specific anthropometric trends.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- Consumers should be cautious about generalizing findings beyond female U.S. Army personnel, as the dataset is not representative of broader populations.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The dataset should not be used for identifying individuals or making decisions that could unfairly impact subgroups without additional validation.
6. *Any other comments?*
	- No.

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes, the dataset is publicly available and can be accessed by researchers or institutions interested in anthropometric studies or military health monitoring.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is distributed via Data World (https://data.world/datamil/ansur-ii-female). It does not have a DOI.
3. *When will the dataset be distributed?*
	- The dataset has already been distributed and is publicly accessible.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset is distributed under a public license with terms outlined on the Data World platform. There are no fees associated with its use for research purposes.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- Cannot find any.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No export controls or regulatory restrictions apply to the dataset.
7. *Any other comments?*
	- The dataset is easily accessible and designed for educational and research purposes.

>>>>

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to investigate the relationship between body weight and anthropometric and demographic predictors among female U.S. Army personnel. It addresses the gap in research on female military personnel, particularly concerning their health, operational readiness, and body composition.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was created by the Natick Soldier Research, Development, and Engineering Center (NSRDEC) on behalf of the U.S. Army as part of the 2012 ANSUR II survey.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The dataset was funded by the U.S. Department of Defense as part of its efforts to improve operational readiness and health monitoring among military personnel.
4. *Any other comments?*
    - This dataset is one of the most comprehensive anthropometric surveys conducted on military personnel, focusing specifically on female soldiers.

@@

	- The dataset contains a total of 1,986 instances, each representing a female U.S. Army personnel. These instances include detailed anthropometric and demographic measurements.

@@

	- Yes, the dataset includes a target variable, weightlbs, which represents the body weight of each individual in pounds. This variable serves as the dependent variable in analyses aiming to understand the relationship between body weight and various anthropometric and demographic predictors.

@@

	- Yes, this research uses an 80/20 split, with 80% of the data used as the training set and 20% as the testing set. This approach ensures that the model is trained effectively on a majority of the data while retaining a portion for unbiased performance evaluation, as demonstrated by the comparison of RMSE between the full and reduced models.

@@

	- Yes, the dataset may have sources of noise such as measurement variability due to inconsistencies in using instruments like calipers and tape measures, as well as missing values that can affect data completeness. These issues were addressed by standardizing measurements and removing rows with missing values during preprocessing to ensure accuracy and reliability.

@@

	- The dataset is largely self-contained and does not rely on external resources for its core variables, as all data were collected directly through the 2012 ANSUR II Female Dataset. While the dataset includes demographic information cross-referenced with administrative records, there are no dependencies on external, dynamically changing resources such as websites or social media. The dataset is publicly available and distributed under terms that do not impose restrictions, ensuring accessibility for researchers without licensing fees or additional conditions. The archival version of the dataset, as it existed at the time of creation, is well-documented and maintained for consistency.

@@

	- No, the dataset does not contain data that would typically be considered confidential. It includes anthropometric and demographic measurements collected from U.S. Army personnel under standardized protocols, but no sensitive personal identifiers or non-public communications are present. The data were anonymized to protect individual privacy, ensuring compliance with ethical and legal standards.

@@

	- Incorporating additional lifestyle variables such as physical activity levels or dietary habits could enhance its utility and explanatory power in future research.

@@

	- The data was collected as part of the 2012 ANSUR II survey conducted by the Natick Soldier Research, Development, and Engineering Center. The timeframe of data collection aligns with the creation of the dataset, as all measurements and associated demographic information were recorded during the survey period in 2012 using standardized protocols. There is no mismatch between the data collection and creation timeframes.

@@

	- The dataset originates from the 2012 ANSUR II survey, conducted by the Natick Soldier Research, Development, and Engineering Center, which followed rigorous ethical standards for data collection. Although specific details about an institutional review board (IRB) review are not explicitly mentioned, the data collection adhered to military protocols ensuring participant confidentiality and informed consent. These procedures are consistent with ethical guidelines for research involving human subjects in military contexts. Supporting documentation, such as the official survey reports, may provide further details and can be accessed through sources like the Natick Soldier Research Center or related publications.

@@

	- The data was obtained by me from the platform Data World, where the 2012 ANSUR II survey dataset is publicly available.

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- No, the dataset has not been used for any specific tasks prior to this analysis. It was obtained for the purpose of exploring the relationship between body weight and key anthropometric and demographic predictors. 
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	-No, there is no repository that links to papers or systems that use this dataset. It was obtained from Data World and does not have an associated archive for tracking its usage in research or systems. 
3. *What (other) tasks could the dataset be used for?*
	- The dataset could be used for health monitoring, ergonomic research, fitness program optimization, and studies on gender-specific anthropometric trends.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- Consumers should be cautious about generalizing findings beyond female U.S. Army personnel, as the dataset is not representative of broader populations.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The dataset should not be used for identifying individuals or making decisions that could unfairly impact subgroups without additional validation.
6. *Any other comments?*
	- No.

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes, the dataset is publicly available and can be accessed by researchers or institutions interested in anthropometric studies or military health monitoring.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is distributed via Data World (https://data.world/datamil/ansur-ii-female). It does not have a DOI.
3. *When will the dataset be distributed?*
	- The dataset has already been distributed and is publicly accessible.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset is distributed under a public license with terms outlined on the Data World platform. There are no fees associated with its use for research purposes.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No, there are no IP-based or other restrictions imposed by third parties on the data associated with the instances. The dataset is publicly available on the Data World platform without licensing terms or fees restricting its use.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No export controls or regulatory restrictions apply to the dataset.
7. *Any other comments?*
	- The dataset is easily accessible and designed for educational and research purposes.
